A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-28 reviews/response.Rmd

> I hold a similar sentiment regarding the calendar plot in Figure 12. It's a great plot but I don't necessary think this is a plot that show cased the benefit of tsibble.

Yes, the calendar plot just requires a data frame. We've added the forecasting example to back up this plot: how the weather information improves the demand forecasts.

> Figure 11 with missing data was a great demonstration for tsibble and the data times series pipeline shown in Figure 3. It may be helpful to reduce the opacity of the points as there is a lot of overplotting. The top line which lumps a number of customers together is not particularly informative here. Perhaps it is better replaced with a histogram.

Thanks. We separated the remaining customers to the bottom panel with points of some transparency. We have kept the line range plot instead of a histogram. Because the range plot is more informative: individual missings are congregated between January and March with sporadic continuous missings over the rest of the year.

@@

> Figure 4 animation doesn't play so authors may like to ensure that the final publication works. Github version works.

Thanks for pointing it out. We include a gif version of the animation as supplementary materials.

> Have the authors thought about how to deal with mixed time resolutions for index? E.g. some subjects have exact day recorded; some missing day but month & year recorded; some only date range recorded.

We have rewritten Section 3.3 to better explain intervals and address the mixed time resolutions.

### 2019-08-28 tsibble.Rmd
rm redundant "" and updated response

The choice of tidy representation of temporal data arises from a data- and model-oriented perspective, which can accommodate all of the operations that are to be performed on the data in time-based contexts. Figure \@ref(fig:tsibble-fit) marks where this new abstraction is placed in the "tidy" model, which is referred to as a "tsibble". Adapting the "tidy data" principles, in tsibble:

@@

Figure \@ref(fig:tsibble-semantics) sketches out the data form required for a tsibble, an extension of the "tidy" format to the time domain. Beyond the layout, tsibble gives the contextual meaning to variables in order to construct the temporal data object, as newly introduced "index" and "key" semantics stated in the definitions 1 and 2 above. Variables other than "index" and "key" are considered as measurements. The definitions of 3 and 4 imply that tsibble is *tidier* than "tidy data", positioning itself as a model input that gives rise to more robust and reliable downstream analytics.

@@

To materialize the abstraction of the tsibble, a subset of tuberculosis cases [@tb-data], as presented in Table \@ref(tab:tb-sub), is used as an example. It contains 12 observations and 5 variables landing in a tidy data form. Each observation comprises the number of people who are diagnosed with tuberculosis for each gender at three selected countries in the years of 2011 and 2012. From tidy data to tsibble data, "index" and "key" should be declared: column `year` as the "index" variable, and column `country` together with `gender` as the "key" variable forming the observational units. Column `count` is the only measured variable in this data, but the data structure is sufficiently flexible to hold more measurements; for example, slotting the corresponding population size (if known) into the data column for normalizing the count later. Note, this data further satisfies the must-have for the distinct rows determined by index and key, and regularly spans over one-year intervals.

@@

What subjects/entities are to be observed over time, leads to the second component of a tsibble--key. The key can consist of empty, single, or multiple variables identifying units measured along the way. When only a single observational unit is present in the table, no key needs to be specified. However, when multiple units exist in the data, the key should be supplied by identifying variables to sufficiently define the units. In longitudinal data, the key can be thought of as "panel" (such as in the Stata) but constrained to a single variable in existing data structures. In tsibble, the key allows for multiple variables of nesting, crossing, or union relations [@wilkinson2006grammar], that can be useful for forecasting reconciliation [@fpp; @R-hts] and richer visualization. For example, Table \@ref(tab:tb-sub) describes the number of tuberculosis cases for each gender across the countries every year. This suggests that the key comprises at least columns `gender` and `country`. Since `country` is nested within `continent`, continent can be included in the key specification, but is not needed.

@@

Inspired by a "primary key" [@codd_relational_1970], a unique identifier for each observation in a relational database, the tsibble key also uniquely identifies each observational unit over time. When constructing a tsibble, any duplicates of key-index (i.e. key-value) pairs will fail, because duplicates signal a data quality issue, which would likely affect subsequent analyses and hence decision making. For example, either `gender` or `country` alone is not enough to be the key for the tuberculosis data. Analysts are encouraged to better understand the data, or reason about the process of data cleaning when handling duplicates. Figure \@ref(fig:tsibble-tidy) peels the "tidy" module with clear routes required for a tsibble. The rigidity of tsibble, as the fundamental data infrastructure, warrants the validity of temporal data analysis for the later stage.

@@

(ref:tsibble-tidy-cap) Details about the "tidy" stage for a tsibble. Built on top of "tidy data", each observation should be uniquely identified by index and key, thereby no duplicated key-index pairs.

@@

To abide by the "tidy data" rules -- "Each type of observational units should form a table" -- in a tisbble each observational unit shares a common interval. This means that a tsibble will report one single interval, whether the data has a fixed or mixed set of intervals. To handle mixed interval data, it should be organized into separate tsibbles for a well-tailored analysis.

>>>>

The choice of tidy representation of temporal data arises from a data- and model-oriented perspective, which can accommodate all of the operations that are to be performed on the data in time-based contexts. Figure \@ref(fig:tsibble-fit) marks where this new abstraction is placed in the tidy model, which is referred to as a "tsibble". Adapting the "tidy data" principles, in tsibble:

@@

Figure \@ref(fig:tsibble-semantics) sketches out the data form required for a tsibble, an extension of the tidy format to the time domain. Beyond the layout, tsibble gives the contextual meaning to variables in order to construct the temporal data object, as newly introduced "index" and "key" semantics stated in the definitions 1 and 2 above. Variables other than index and key are considered as measurements. The definitions of 3 and 4 imply that tsibble is *tidier* than tidy data, positioning itself as a model input that gives rise to more robust and reliable downstream analytics.

@@

To materialize the abstraction of the tsibble, a subset of tuberculosis cases [@tb-data], as presented in Table \@ref(tab:tb-sub), is used as an example. It contains 12 observations and 5 variables landing in a tidy data form. Each observation comprises the number of people who are diagnosed with tuberculosis for each gender at three selected countries in the years of 2011 and 2012. From tidy data to tsibble data, index and key should be declared: column `year` as the *index* variable, and column `country` together with `gender` as the *key* variable forming the observational units. Column `count` is the only measured variable in this data, but the data structure is sufficiently flexible to hold more measurements; for example, slotting the corresponding population size (if known) into the data column for normalizing the count later. Note, this data further satisfies the must-have for the distinct rows determined by index and key, and regularly spans over one-year intervals.

@@

What subjects/entities are to be observed over time, leads to the second component of a tsibble--key. The key can consist of empty, single, or multiple variables identifying units measured along the way. When only a single observational unit is present in the table, no key needs to be specified. However, when multiple units exist in the data, the key should be supplied by identifying variables to sufficiently define the units. In longitudinal data, the key can be thought of as "panel" (such as in the Stata) but constrained to a single variable in existing data structures. In tsibble, the key allows for multiple variables of nesting, crossing, or union relations [@wilkinson2006grammar], that can be useful for forecasting reconciliation [@fpp; @R-hts] and richer visualization. For example, Table \@ref(tab:tb-sub) describes the number of tuberculosis cases for each gender across the countries every year. This suggests that the key comprises at least columns `gender` and `country`. Since `country` is nested within `continent`, `continent` can be included in the key specification, but is not compulsory.

@@

Inspired by a "primary key" [@codd_relational_1970], a unique identifier for each observation in a relational database, the tsibble key also uniquely identifies each observational unit over time. When constructing a tsibble, any duplicates of key-index (i.e. key-value) pairs will fail, because duplicates signal a data quality issue, which would likely affect subsequent analyses and hence decision making. For example, either `gender` or `country` alone is not enough to be the key for the tuberculosis data. Analysts are encouraged to better understand the data, or reason about the process of data cleaning when handling duplicates. Figure \@ref(fig:tsibble-tidy) peels the tidy module with clear routes required for a tsibble. The rigidity of tsibble, as the fundamental data infrastructure, warrants the validity of temporal data analysis for the later stage.

@@

(ref:tsibble-tidy-cap) Details about the tidy stage for a tsibble. Built on top of "tidy data", each observation should be uniquely identified by index and key, thereby no duplicated key-index pairs.

@@

To abide by the "tidy data" rules -- "Each type of observational units should form a table" -- in a tsibble each observational unit shares a common interval. This means that a tsibble will report one single interval, whether the data has a fixed or mixed set of intervals. To handle mixed interval data, it should be organized into separate tsibbles for a well-tailored analysis.
